Visualizing probability distributions across bivariate nonlinear temporal granularities

### 2020-02-13 main.Rmd
spell check

Linear time granularities respect the linear progression of time such as hours, days, weeks and months, and non-repeating. One of the first attempts to characterize these granularities is due to @Bettini1998-ed. However, the definitions and rules defined are inadequate for describing nonlinear or repeating granularities. Hence, there is a need to define some new nonlinear time granularities, that can be useful in visualizations. Nonlinear time granularities can be circular, quasi-circular or aperiodic. Examples of circular granularities are hour of the day and day of the week; an examples of a quasi-circular granularty is day of the month; examples of aperiodic granularities are public holidays and school holidays.

@@

```{r group-periodicial, echo=FALSE, out.width = "100%", fig.cap="Linear granularity $B$ groups periodically into linear granularity $G$ with $P = 5$ and $R = 2$, alternating between combining 2 and 3 granules of $B$."}
knitr::include_graphics("Figs/groups_periodically.png")
```

@@

```{r quasi-group-periodicial, echo=FALSE, out.width = "100%", fig.cap="Linear granularity $B$ groups quasi-periodically into linear granularity $G$ with $P = 5$ and $R = 2$, alternating between combining 2 and 3 granules of $B$ with $E1$ as the exception."}
knitr::include_graphics("Figs/quasi_groups_periodically.png")
```

**Example**:  Example showing periodic and quasi-periodic linear granularities are displayed in \autoref{fig:group-periodicial} and \autoref{fig:quasi-group-periodicial} respectively. Each granule is represented by a box. In these figures, the granules that overlap share elements from the underlying time domain. In both of these cases, each granule of $G$ is made up of two and three granules of $B$ alternately. So the period is $P = 5$ and number of granules of $G$ in each period is given by $R=2$. The only difference in \autoref{fig:quasi-group-periodicial} is that there is an exception after the first granule of $G$ which consists of one granule of $B$. Except for this exception $E1$, $B$ groups periodically into $G$.

@@

\todo[inline]{What does "full-integer" mean? It might be the case that we don not always
have integers as the label sets of granularities. A full-integer labeled granularities are defined in definition 2 since labels coincide with indices. These labels can be an
arbitrary subset of (possibly noncontiguous) integers and could be used to identify granules. The author has introduced the definition of "labeled granularity" in @Ning2002-tf which could be added after definition of linear granularity to clarify this. }

>>>>

Linear time granularities respect the linear progression of time such as hours, days, weeks and months, and non-repeating. One of the first attempts to characterize these granularities is due to @Bettini1998-ed. However, the definitions and rules defined are inadequate for describing nonlinear or repeating granularities. Hence, there is a need to define some new nonlinear time granularities, that can be useful in visualizations. Nonlinear time granularities can be circular, quasi-circular or aperiodic. Examples of circular granularities are hour of the day and day of the week; an examples of a quasi-circular granularity is day of the month; examples of aperiodic granularities are public holidays and school holidays.

@@

```{r group-periodical, echo=FALSE, out.width = "100%", fig.cap="Linear granularity $B$ groups periodically into linear granularity $G$ with $P = 5$ and $R = 2$, alternating between combining 2 and 3 granules of $B$."}
knitr::include_graphics("Figs/groups_periodically.png")
```

@@

```{r quasi-group-periodical, echo=FALSE, out.width = "100%", fig.cap="Linear granularity $B$ groups quasi-periodically into linear granularity $G$ with $P = 5$ and $R = 2$, alternating between combining 2 and 3 granules of $B$ with $E1$ as the exception."}
knitr::include_graphics("Figs/quasi_groups_periodically.png")
```

**Example**:  Example showing periodic and quasi-periodic linear granularities are displayed in \autoref{fig:group-periodical} and \autoref{fig:quasi-group-periodical} respectively. Each granule is represented by a box. In these figures, the granules that overlap share elements from the underlying time domain. In both of these cases, each granule of $G$ is made up of two and three granules of $B$ alternately. So the period is $P = 5$ and number of granules of $G$ in each period is given by $R=2$. The only difference in \autoref{fig:quasi-group-periodical} is that there is an exception after the first granule of $G$ which consists of one granule of $B$. Except for this exception $E1$, $B$ groups periodically into $G$.

@@

\todo[inline]{What does "full-integer" mean? It might be the case that we do not always
have integers as the label sets of granularities. A full-integer labeled granularities are defined in definition 2 since labels coincide with indices. These labels can be an
arbitrary subset of (possibly non contiguous) integers and could be used to identify granules. The author has introduced the definition of "labeled granularity" in @Ning2002-tf which could be added after definition of linear granularity to clarify this. }
